Supervised Learning for Psychological Attention to High School Students

### 2020-11-18 article/inputs/svm.tex
[ article ] Complemented idea.

The Linear Kernel SVM had the worst performance in comparison to the others.
This fact can be seen in Table \ref{tab:linear_SVM}, in which is observed that
this machine does not classify any data point to the class 1.

>>>>

The Linear Kernel SVM had the worst performance in comparison to the others.
This fact can be seen in Table \ref{tab:linear_SVM}, in which is observed that
this machine does not classify any data point to the class 1 as the sensitivity
value is 0 for the three datasets.
